\chapter{Preface}
	
This document (\texttt{\docno}) serves as the \gls{pdr} for the University of Illinois at Urbana-Champaign University Student Launch Initiative team, \gls{iss}. The content of this report will chiefly focus on the changes since the original proposal, developments in design and underlying justifications, as well as overall prospects and plans towards the \gls{cdr}. In particular, the launch vehicle design is detailed with reference to the pertinent vehicle requirements, providing an overview of its subsystems, interfaces, and manufacturing methods. Safety considerations are addressed through a multitude of simulations, as well as a qualitative \gls{fmea} and \gls{eia}. Following this discussion, the payload requirements and preliminary design of both the airframe and sample retrieval mechanism are presented, culminating in the presentation of a detailed \gls{conops}. The payload--launch vehicle interface as well as the aerial deployment mechanism are discussed, giving rise to a detailed safety analysis. As part of the safety analysis, in addition to a comprehensive \gls{fmea}, a \gls{pha} is presented. Any hazardous activities will be identified as part of this discussion, including any foreseeable contingencies and mitigation procedures. Finally, a project plan is presented, including a project timeline (Gantt chart), bill of materials, list of funding sources and mitigation procedures in case of delays.

This report is composed of six parts, in which each part builds forth upon the previous. These parts are:

\begin{enumerate}[noitemsep, label=\Roman*]
	\item Summary
	\item Changes
	\item Launch Vehicle
	\item Payload
	\item Safety
	\item Project Plan
\end{enumerate}

Each of these parts describes in due detail the developments and rationale behind the launch vehicle and payload design, as well as the overall implementation.

\paragraph{DISCLAIMER:}
While the authors have gone through great lengths to ensure the validity of all data presented in this document, all responsibility is assumed for any inconsistencies presented as part of this work. 